Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-02-06 manuscript/manuscript.Rmd
Added computation for robustness comparison.

@@

# Generate table of asymmetric generalised normal distribution parameters.
n_distributions <- 10

@@

experiments <- coro::collect(experiment_args())

# Function for computing transformer parameters under optimisation constraints.
compute_robust_lambda <- function(
    x,
    fun_args,
    opt_args){

@@

  parameter_data <- lapply(
    x,
    ..outlier_parser,
    fun_args = fun_args,
    opt_args = opt_args)

@@

# Inner optimisation function that sets the loss.
..optimisation_function <- function(
  opt_param,
  x,
  fun_args){

@@

  parameter_data <- compute_robust_lambda(
    x = x,
    fun_args = fun_args,
    opt_args = opt_args)

@@

# Outer optimisation function
.optimisation_function <- function(
    experiment,
    x){

@@

    h <- nloptr::sbplx(
      x0 = x0,
      fn = ..optimisation_function,
      lower = lower,
      upper = upper,
      control=list("xtol_rel"=1e-3, "ftol_rel"=1e-4),
      x = x,
      fun_args = experiment$fun_args)

@@

  } else {
    value <- ..optimisation_function(
      opt_param=list(),
      x = x,
      fun_args=experiment$fun_args)

@@

lapply(
  experiments,
  .optimisation_function,
  x=x
)

>>>>

manuscript_dir <- file.path(
  getwd())

@@

# Generate table of asymmetric generalised normal distribution parameters.
n_distributions <- 100

@@

# Function for computing transformer parameters under optimisation constraints.
compute_robust_lambda <- function(
    x,
    fun_args,
    opt_args,
    cl=NULL){

@@

  if(is.null(cl)){
    parameter_data <- lapply(
      x,
      ..outlier_parser,
      fun_args = fun_args,
      opt_args = opt_args)

  } else {
    parameter_data <- parallel::parLapply(
      cl = cl,
      X = x,
      fun = ..outlier_parser,
      fun_args = fun_args,
      opt_args = opt_args)
  }

@@

# Inner optimisation function that sets the loss.
..optimisation_function <- function(
  opt_param,
  x,
  fun_args,
  cl = NULL){

@@

  parameter_data <- compute_robust_lambda(
    x = x,
    fun_args = fun_args,
    opt_args = opt_args,
    cl = cl)

@@

# Outer optimisation function
.optimisation_function <- function(
    experiment,
    x,
    cl = NULL){

@@

    h <- nloptr::sbplx(
      x0 = x0,
      fn = ..optimisation_function,
      lower = lower,
      upper = upper,
      control=list("xtol_rel"=1e-3, "ftol_rel"=1e-4),
      x = x,
      fun_args = experiment$fun_args,
      cl = cl)

@@

  } else {
    value <- ..optimisation_function(
      opt_param=list(),
      x = x,
      fun_args=experiment$fun_args,
      cl = cl)

@@

experiment_results <- lapply(
  coro::collect(experiment_args()),
  .optimisation_function,
  x = x,
  cl = cl)
